### 2016-11-22 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
Eds

Fig2B <- transform(dd3,Cohort = factor(LayYear)) %>%
  subset(Cohort %in% c(2002:2011)) %>%
  ggplot(aes(y = RTL,x = DeltaAge, col = Cohort))+
  xlab('Age (years)') +
  geom_smooth(method = 'lm', formula = y~(x),se = F) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none') +
    scale_color_manual(values = c15)+
  annotate('text',x = 0,y = 1.15,label = 'B')

Fig2D <- transform(dd,Cohort = factor(CatchYear)) %>%
  subset(Cohort %in% c(2002:2011)) %>%
  ggplot(aes(y = RTL,x = DeltaAge, col = Cohort))+
  xlab('Age (years)') +
  geom_smooth(method = 'lm', formula = y~(x),se = F) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none') +
    scale_color_manual(values = c15)+
  annotate('text',x = 0,y = 1.15,label = 'D')

@@

>>>>

Fig2A <- transform(dd,Cohort = factor(LayYear)) %>%
  subset(Cohort %in% c(2002:2011)) %>%
  ggplot(aes(y = RTL,x = Cohort,fill = Cohort))+
  xlab('Birth year') +
  geom_boxplot(notch=T,aes(outlier.colour = Cohort)) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12,angle = 90), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none')+
  scale_fill_manual(values = c15)+
  annotate('text',x = 1,y = 1.7,label = 'A')

Fig2B <- transform(dd3,Cohort = factor(LayYear)) %>%
  subset(Cohort %in% c(2002:2011)) %>%
  ggplot(aes(y = RTL,x = Agemonths, col = Cohort))+
  xlab('Age (years)') +
  geom_smooth(method = 'lm', formula = y~log(x),se = F) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none') +
    scale_color_manual(values = c15)+
  annotate('text',x = 0,y = 1.15,label = 'B')

pdf('Figures/Figure 2.pdf',
    width = 4,
    height = 8,
    paper = 'a4')
multiplot(Fig2A,Fig2B)
dev.off()

@@

dd$FAge <- factor(dd$Agemonths)
dd$Cohort <- factor(dd$LayYear)

lm1 <- lmer(RTL ~ Cohort*(Agemonths + LogAge + FAge) + (1|BirdID) + (1|CatchYear) + (1|PlateID),data=dd,REML = FALSE)

lm2 <- dredge(lm1,subset = !(LogAge & FAge) & !(LogAge & Agemonths ) & !(Agemonths & FAge))

lm2
